\speculake: Hiding Malware in Speculative Execution

### 2018-05-01 paper/payloads.tex
update encryption model

@@

\subsection{Turing Machine}
\label{subsec:turing}
- Arbitrary computation

\subsection{Unpacking and Decryption}
\label{subsec:decryption}
- AES instructions

@@

\subsection{Virtual Machines}
Given the specific constraints that the speculative environment enforces on these 
paylods, general purpose compuatation []. We demonstrated in section~\ref{subsec:turing} that 
general purpose computation is possible using computation performed in the 
speculative environment. However, a turing machine is not a user friendly model,
nor is it an efficient model for computation when attempting to accomplish tasks
on modern processors.

Using emulators in the "real world" allows for crafted binary programs to be 
instrumented in dead code and, as demonstrated in secton~\ref{subsec:decryption} 
encrypted and hidden. This gives an advantage to attackers as traditional 
reverse engineering methods will reveal only that emulation is being done. 
It reveals nothing about the ultimate goal of the program.

>>>>

Next, we observe that the instructions to be executed speculatively can be
obscured further by encrypting them. This encryption allows for hidden
computation, instructions are stored in the real world encrypted, they are then
decrypted in the speculative world and passed to the real world to be executed.
This method makes it appear as though the program is generating its own code.

@@

\subsection{Turing Machine}
\label{subsec:turing}
To demonstrate that arbitrary computation can be done in the speculative world
we create a Turing Machine to compute a 6 state Busy Beaver Turing Machine.

\subsection{Unpacking and Decryption}
\label{subsec:decryption}
While Section \ref{subsec:turing} demonstrates that arbitrary computation is
possible, if a reverse engineer can discover the \emph{speculative instructions}
they can determine the execution of the program by simply reading the
instructions that are to be executed speculatively. To avoid this these
instructions can be encrypted, meaning that a reverse engineer can never
determine these instructions by examining the ELF file, or generating source
code.

In order for these instructions to be executed they must be decrypted. We wish
to obscure the fact that we are using encrypted instructions from the ``real
world'', thus  the speculative world must do the decryption.

Any observer watching the execution of this program would never see any
indication of decryption, due to the exploitation of speculative execution. Any
observation of the executed instructions would not include any of the decryption
instructions, or loading of keys as they are only done speculatively, and thus
not shown in any debugging or real world traces of program execution.
Additionally the observer would be unable to find the executed instructions in
the ELF file as they are only stored encrypted.

There are numerous challenges for a reverse engineer to overcome to learn how a
malicious program with this primitive works. As with previous examples, the
malicious instructions are only executed when the correct trigger program is
running (priming the jump table predictor \textbf{TK: word for this?}). However,
when the to-be-executed instructions are executed the reverse engineer cannot
locate these instructions in the ELF file, or generated source code. These
instructions (when they even appear) seem to be generated by themselves, with no
apparent cause. Additionally, there is no indicator that these instructions are
encrypted as the decryption is done in the speculative world, meaning that no
decryption (or key interaction) is done in a way visible to a reverse engineer.

This method allows for arbitrary computation that is unobservable to any observer (static or dynamic).

@@

\subsection{Virtual Machines}
Given the specific constraints that the speculative environment enforces on
these payloads, general purpose computation []. We demonstrated in
Section~\ref{subsec:turing} that general purpose computation is possible using
computation performed in the speculative environment. However, a turing machine
is not a user friendly model, nor is it an efficient model for computation when
attempting to accomplish tasks on modern processors.

Using emulators in the "real world" allows for crafted binary programs to be
instrumented in dead code and, as demonstrated in
Section~\ref{subsec:decryption} encrypted and hidden. This gives an advantage to
attackers as traditional reverse engineering methods will reveal only that
emulation is being done. It reveals nothing about the ultimate goal of the
program.
